---
title: "5-Homework Using `dplyr` and `ggplot2`"
subtitle: Conducting a t-test to compare two independent groups.
output:
  #pdf_document: default #prevents ability to download .rmd file in html notebook
  html_document: default # don't use for distribution; tibble is truncated in html view
  code_download: FALSE
---
You will need these libraries:
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
```
<br />
You will need this data:
```{r}
data(msleep)
```
<br />
<br />
**Question 1**. Use `dplyr` to recreate the summary table below using the `msleep` dataset (built into ggplot). You will need to use several of the `dplyr` verbs (functions) we have learned in class. Your full table should have 17 rows (although fewer rows may be displayed by default).
<br />
<br />
```{r echo=FALSE}
data_summary <- msleep %>% filter(order == "Rodentia" | order == "Carnivora") %>%
  filter(brainwt>0) %>%
  select(name, order, brainwt, bodywt) %>%
  mutate(ratio=brainwt/bodywt) %>%
  arrange(desc(bodywt))
data_summary
```
<br />
<br />
**Question 2**. Use a t-test to compare the two mammal orders, Rodentia and Carnivora, in their ratio of brain weight to body weight.
Format your answer as you would see in the results section of a scientific journal article. 
<br />
<br />
```{r eval=FALSE, include=FALSE}
t.test(data=data_summary, ratio~order)
```
<br />
**Question 3**. Using `ggplot2`, replicate the following figure. Fill in the values from your t-test (Question 2).
```{r echo=FALSE}
ggplot(data_summary, aes(x = order, y = ratio)) +
  geom_boxplot() +
  geom_point(size = 4, color = 'red', alpha = 0.5) +
  labs(x = "Mammalian Order", y = "Ratio of Brain Weight to Body Weight")+
  annotate("text", x = 1.5, y = 0.035, label = "t = ?, df = ?, P = ?")
```
<br />
<br />
**Question 4**. Save the plot to your Rproject folder for this exercise as a 6" X 6" .jpg file.
```{r eval=FALSE, include=FALSE}
ggsave("CoolMammalPlot.jpg", width = 6, height = 6)
```

Homework (folder containing .rproj file and all associated input/output files) is due to the D2L Assignments dropbox **before class one week from today**.
<br />
<br />
<br />
As before, make each of your 'answers' an object. (e.g.)
Answer_3 <- ggplot(data_summary, aes(x = ........ and 'print' the name of the object below the specified code (e.g. Answer_3). Each object is then displayed automatically in the console (if a model or table) or plot viewer (if its a graph) without having to click on anything. 